---
name: "Eric R. Scott, PhD"
position: "Postdoctoral Associate"
address: "University of Florida"
phone: +1 925-788-9855
www: ericrscott.com
email: ericscott@ufl.edu
twitter: LeafyEricScott
github: Aariq
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
---

Updated `r Sys.Date()`

```{r eval=FALSE, include=FALSE}
# Remember to spell check!!
data_files <- list.files(here("data"), pattern = ".csv", full.names = TRUE)
spelling::spell_check_files(c("CV.Rmd", data_files))
```

```{r eval=FALSE, include=FALSE}
# To update CV on my website, run the following code in the console:
rmarkdown::render("CV.Rmd", output_file = "/Users/scottericr/Documents/Blogdown/website2/static/files/Eric Scott cv.pdf")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
library(conflicted)
conflict_prefer("filter", "dplyr")
conflict_prefer("here", "here")
```

```{r experience, inclue=FALSE}
jobs.raw <- read_csv(here::here("data", "jobs.csv"))
jobs <-
  jobs.raw %>% 
  fill(Start, End, What, With, Where, Tag) %>%  
  mutate(Start = mdy(Start),
         End = mdy(End)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  )) %>% 
  mutate(End = if_else(is.na(End), today() + years(2), End)) #if no end date specified, set it to two years from now for sorting purposes, i.e. so jobs I'm still doing show up at top.
```

```{r presentations, include=FALSE}
presentations.raw <- read_csv(here("data", "presentations.csv"))
presentations <- 
  presentations.raw %>% 
  mutate(When = mdy(When)) %>% 
  filter(When < today()) #exclude upcoming talks
```

```{r prof-devel, include=FALSE}
development.raw <- read_csv(here("data", "professional development.csv"))
development <- 
  development.raw %>% 
  mutate(date = mdy(date))
```

```{r awards, include=FALSE}
awards.raw <- read_csv(here("data", "awards and grants.csv"))
awards <- awards.raw %>% 
  mutate(date = mdy(date)) %>% 
  arrange(desc(date))
```

```{r edu, include=FALSE}
edu.raw <- read_csv(here("data", "education.csv"))
edu <-
  edu.raw %>% 
  mutate(pi = if_else(!is.na(pi), glue("PI: {pi}"), as.character(NA)),
         dissertation = glue("\\textbf{[dissertation]}", .open = "[", .close = "]")) %>% 
  gather(dissertation, pi, key = "whytype", value = "why")
edu["why"]
```

```{r outreach, include=FALSE}
outreach.raw <- read_csv(here("data", "outreach.csv"))
outreach <- outreach.raw %>% mutate(sortdate = mdy(sortdate))

```

# Education

```{r}
detailed_entries(edu, 
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = location,
                 with = university,
                 why = why,
                 .protect = FALSE)

```


```{=html}
<!--# Teaching Interests
A sentence or two about the sorts of courses I'd like to teach.  Tailor to each job application
-->
```

# Teaching Experience
 
```{r}
jobs %>%
  filter(Tag == "teaching", year(Start) > 2005) %>%
  arrange(desc(Start)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why, .protect = FALSE)
```
  
## Guest Lectures

```{r}
presentations %>% 
  filter(Tag %in% c("lecture")) %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}") %>% as.character(),
                   with = Conference,
                   where = Location,
                   why = Award)
```
## Training and Professional Development

```{r}
development %>% 
  filter(str_detect(tag, "teaching") | str_detect(tag, "dei")) %>% 
  arrange(desc(date)) %>% 
  brief_entries(
    what = title,
    when = glue("{month(date, label = TRUE)} {year(date)}"),
    with = location,
    .protect = FALSE
  )
```

# Research Experience

```{r research}
jobs %>% 
  filter(Tag == "research") %>% 
  # arrange(desc(Start)) %>%
  arrange(desc(End)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    why = Why,
    .protect = FALSE
  )
```

# Grants

```{r}
awards %>%
  filter(tag == "grant") %>%
  detailed_entries(what = award, when = glue("{month(date, label = TRUE)} {year(date)}"),
                   why = amount) %>% 
  mutate_all(as.character) %>% 
  mutate(with = as.character(with),
         when = as.character(when),
         where = as.character(where))
```

# Awards and Honors

```{r}
 awards %>% 
  filter(!tag %in% c("failed", "travel", "grant")) %>% 
  brief_entries(what = award, when = glue("{month(date, label = TRUE)} {year(date)}"), with = with)
```

# Publications

^\*^ indicates undergraduate mentee author

```{r publications}
scholar::get_publications("kPEDEO0AAAAJ", flush = TRUE) %>%
  mutate(author = str_replace_all(author, "MM Guo", "MM Guo*"),
         author = str_replace_all(author, "A Agyei", "A Agyei*")) %>% 
  arrange(desc(year)) %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

## Software
<!-- Would be good to update these soon -->
```{r}
df <- tribble(~what, ~when, ~with, ~where, ~why,
              "bumbl: Tools for modeling bumblebee colony growth",
              2021,
              "ER Scott, E Crone",
              "https://cran.r-project.org/package=bumbl",
              "Author and maintainer",
              
              "webchem: retrieve chemical information from the web",
              2020,
              "E Szöcs, D Muench, J Ranke, ER Scott, J Stanstrup, R Allaway, Tamas Stirling",
              "https://cran.r-project.org/web/packages/webchem/",
              "Contributor and maintainer",
              
              "holodeck: A tidy interface for simulating multivariate data",
              2018,
              "ER Scott",
              "https://cran.r-project.org/web/packages/holodeck/",
              "Author and maintainer"
              )
```

```{r}
df %>% 
  arrange(desc(when)) %>% 
  detailed_entries(what = what, when = when, with = with, where = where, why = why)
```

# Presentations

## Research Talks

```{r}
presentations %>% 
  filter(Tag %in% c("talk", "invited")) %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Conference,
                   where = Location,
                   why = Award,
                   .protect = FALSE)
```

## Posters

```{r}
presentations %>% 
  filter(Tag == "poster") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Conference,
                   where = Location,
                   why = Award,
                   .protect = FALSE)
```

# Outreach

```{r}
outreach %>%
  arrange(desc(sortdate)) %>%
  detailed_entries(when = When,
                   what = Title,
                   with = Organization,
                   where = Location,
                   why = Description)
```

# Service

-   Review Editor for Plant Metabolism and Chemodiversity section of Frontiers in Plant Science

**Manuscript Reviews**

```{r}
#set this up to pull from publons some day.
```

-   Agronomy (1)
-   Journal of Chemical Ecology (1)
-   Ecological Entomology (3)
-   International Journal of Climatology (2)
-   Oecologia (1)
-   Frontiers in Cellular and Infection Microbiology (1)

```{r}
jobs %>%
  filter(Tag == "service") %>% 
  group_by(What) %>% 
  summarize(across(c(When, With, End), first)) %>% 
  arrange(desc(End)) %>% 
    brief_entries(
      what = What,
      when = When,
      with = With
    )
```

## Presented Workshops

```{r}
presentations %>% 
  filter(Tag == "workshop") %>% 
  arrange(desc(When)) %>% 
  brief_entries(
    what = Title,
    when = glue("{month(When, label = TRUE)} {year(When)}"),
    with = Conference,
    # where = Location,
    # why = Award
  )
```

