---
name: "Eric R. Scott, PhD"
position: "Postdoctoral Associate"
address: "University of Florida"
phone: +1 925-788-9855
www: ericrscott.com
email: ericscott@ufl.edu
twitter: LeafyEricScott
github: Aariq
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
urlcolor: blue
---

Updated `r Sys.Date()`

```{r eval=FALSE, include=FALSE}
# Remember to spell check!!
data_files <- list.files(here("data"), pattern = ".csv", full.names = TRUE)
spelling::spell_check_files(c("CV.Rmd", data_files))
```

```{r eval=FALSE, include=FALSE}
# To update CV on my website, run the following code in the console:
rmarkdown::render(here::here("CV", "CV.Rmd"), output_file = "/Users/scottericr/Documents/GitHub/website2/static/files/Eric Scott cv.pdf")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
library(conflicted)
library(bib2df)
library(textutils)
conflict_prefer("filter", "dplyr")
conflict_prefer("here", "here")
conflict_prefer("collapse", "glue")
```

```{r experience, inclue=FALSE}
jobs.raw <- read_csv(here::here("data", "jobs.csv"))
jobs <-
  jobs.raw %>% 
  fill(Start, End, What, With, Where, Tag) %>%  
  mutate(Start = mdy(Start),
         End = mdy(End)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  )) %>% 
  mutate(End = if_else(is.na(End), today() + years(2), End)) #if no end date specified, set it to two years from now for sorting purposes, i.e. so jobs I'm still doing show up at top.
```

```{r presentations, include=FALSE}
presentations.raw <- read_csv(here("data", "presentations.csv"))
presentations <- 
  presentations.raw %>% 
  mutate(When = mdy(When)) %>% 
  filter(When > ymd("2008-01-01")) # filter out really old talks
```

```{r prof-devel, include=FALSE}
development.raw <- read_csv(here("data", "professional development.csv"))
development <- 
  development.raw %>% 
  mutate(date = mdy(date))
```

```{r awards, include=FALSE}
awards.raw <- read_csv(here("data", "awards and grants.csv"))
awards <- awards.raw %>% 
  mutate(date = mdy(date)) %>% 
  arrange(desc(date)) %>% 
  filter(date > ymd("2008-01-01")) #filter out undergrad
```

```{r edu, include=FALSE}
edu.raw <- read_csv(here("data", "education.csv"))
edu <-
  edu.raw %>% 
  mutate(pi = if_else(!is.na(pi), glue("PI: {pi}"), as.character(NA)),
         dissertation = glue("\\textbf{[dissertation]}", .open = "[", .close = "]")) %>% 
  gather(dissertation, pi, key = "whytype", value = "why")
edu["why"]
```

```{r outreach, include=FALSE}
outreach.raw <- read_csv(here("data", "outreach.csv"))
outreach <- outreach.raw %>% mutate(sortdate = mdy(sortdate))

```

# Education

```{r}
detailed_entries(edu, 
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = location,
                 with = university,
                 why = why,
                 .protect = FALSE)

```
# Research Experience

```{=html}
<!--
A sentence or two about my research interests
-->
```

```{r research}
jobs %>% 
  filter(Tag == "research") %>% 
  # arrange(desc(Start)) %>%
  arrange(desc(End)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    # why = Why,
    .protect = FALSE
  )
```

# Publications

^\*^ indicates undergraduate mentee author

\bigskip

```{r eval=FALSE, include=FALSE, results='asis'}
library(RefManageR)
my_pubs <- RefManageR::ReadBib(here("data", "my_publications.bib"))
NoCite(my_pubs)
PrintBibliography(my_pubs, .opts = list(
  sorting = "ydnt",
  style = "markdown",
  bib.style = "authoryear"
))

```

**Scott ER**, Uriarte M, Bruna EM (2021) Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments. Global Change Biology 28:463-479. DOI: [10.1111/gcb.15900](https://doi.org/10.1111/gcb.15900).

\medskip

**Scott ER**, Wei J-P, Li X, Han W-Y, Orians CM (2021) Differing non-linear, lagged effects of temperature and precipitation on an insect herbivore and its host plant. Ecological Entomology 46:866–876. DOI: [10.1111/een.13023](https://doi.org/10.1111/een.13023)

\medskip

Donatelli CM, Roberts AS, **Scott ER**, DeSmith K, Summers D, Abu-Bader L, Baxter D, Standen EM, Porter ME, Summers AP, Tytell ED (2021) Foretelling the flex—vertebral shape predicts behavior and ecology of fishes. Integrative and Comparative Biology. DOI: [10.1093/icb/icab110](https://doi.org/10.1093/icb/icab110)

\medskip

**Scott ER**, Crone EE (2021) Using the right tool for the job: the difference between unsupervised and supervised analyses of multivariate ecological data. Oecologia. DOI: [10.1007/s00442-020-04848-w](https://doi.org/10.1007/s00442-020-04848-w)

\medskip

**Scott ER**, Li X, Wei J-P, Kfoury N, Morimoto J, Guo M-M^\*^, Agyei A^\*^, Robbat A, Ahmed S, Cash SB, Griffin TS, Stepp JR, Han W, Orians CM (2020) Changes in tea plant secondary metabolite profiles as a function of leafhopper density and damage. Frontiers in Plant Science 11:636. DOI: [10.3389/FPLS.2020.00636](https://doi.org/10.3389/FPLS.2020.00636)

\medskip

Szöcs E, Stirling T, **Scott ER**, Scharmüller A, Schäfer RB (2020) webchem: An R Package to Retrieve Chemical Information from the Web. J Stat Soft 93. DOI: [10.18637/jss.v093.i13](https://doi.org/10.18637/jss.v093.i13)

\medskip

**Scott ER**, Li X, Kfoury N, Morimoto J, Han W-Y, Ahmed S, Cash SB, Griffin TS, Stepp JR, Robbat A, Orians CM (2019) Interactive effects of drought severity and simulated herbivory on tea (Camellia sinensis) volatile and non-volatile metabolites. Environmental and Experimental Botany 157:283–292. DOI: [10.1016/j.envexpbot.2018.10.025](https://doi.org/10.1016/j.envexpbot.2018.10.025)

\medskip

Orians CM, Schweiger R, Dukes JS, **Scott ER**, Müller C (2019) Combined impacts of prolonged drought and warming on plant size and foliar chemistry. Annals of Botany 124:41–52. DOI: [10.1093/aob/mcz004](https://doi.org/10.1093/aob/mcz004)

\medskip

Kfoury N, **Scott ER**, Orians CM, Ahmed S, Cash SB, Griffin T, Matyas C, Stepp JR, Han W, Xue D, Long C, Robbat A (2019) Plant-Climate Interaction Effects: Changes in the Relative Distribution and Concentration of the Volatile Tea Leaf Metabolome in 2014–2016. Frontiers in Plant Science 10:1518. DOI: [10.3389/fpls.2019.01518](https://doi.org/10.3389/fpls.2019.01518)

\medskip

Kfoury N, Morimoto J, Kern A, **Scott ER**, Orians CM, Ahmed S, Griffin T, Cash SB, Stepp JR, Xue D, Long C, Robbat A (2018) Striking changes in tea metabolites due to elevational effects. Food Chemistry 264:334–341. DOI: [10.1016/j.foodchem.2018.05.040](https://doi.org/10.1016/j.foodchem.2018.05.040)

\medskip

Li X, Wei J-P, **Scott ER**, Liu J-WJ-W, Guo S, Li Y, Zhang L, Han W-Y (2018) Exogenous Melatonin Alleviates Cold Stress by Promoting Antioxidant Defense and Redox Homeostasis in Camellia sinensis L. Molecules 23:165. DOI: [10.3390/molecules23010165](https://doi.org/10.3390/molecules23010165)

\medskip

**Scott ER**, Orians CM (2018) Differential Changes in Tea Quality as Influenced by Insect Herbivory. In: Han W-Y, Li X, Ahammed GJ (eds) Stress Physiology of Tea in the Face of Climate Change. Springer Singapore, Singapore, pp 217–240

\medskip

Kfoury N, **Scott ER**, Orians C, Robbat A (2017) Direct Contact Sorptive Extraction: A Robust Method for Sampling Plant Volatiles in the Field. Journal of Agricultural and Food Chemistry 65:8501–8509. DOI: [10.1021/acs.jafc.7b02847](https://doi.org/10.1021/acs.jafc.7b02847)

\medskip

Dorchin N, **Scott ER**, Clarkin CE, Luongo MP, Jordan S, Abrahamson WG (2009) Behavioural, ecological and genetic evidence confirm the occurrence of host-associated differentiation in goldenrod gall-midges. Journal of evolutionary biology 22:729–739. DOI: [10.1111/j.1420-9101.2009.01696.x](https://doi.org/10.1111/j.1420-9101.2009.01696.x)

\medskip

Dorchin N, Clarkin CE, **Scott ER**, Luongo MP, Abrahamson WG (2007) Taxonomy, life history, and population sex ratios of North American Dasineura (Diptera: Cecidomyiidae) on goldenrods (Asteraceae). Annals of the Entomological Society of America 100:539–548. DOI: [10.1603/0013-8746(2007)100[539:TLHAPS]2.0.CO;2](https://doi.org/10.1603/0013-8746(2007)100[539:TLHAPS]2.0.CO;2)

\medskip

Dorchin N, **Scott ER**, Abrahamson WG (2006) First record of Macrolabis (Diptera: Cecidomyiidae) in America: A new inquiline species from Dasineura folliculi galls on goldenrods. Annals of the Entomological Society of America 99:656–661. DOI: [10.1603/0013-8746(2006)99[656:FROMDC]2.0.CO;2](https://doi.org/10.1603/0013-8746(2006)99[656:FROMDC]2.0.CO;2)


```{r include=FALSE}

mypubs <-
  #read in .bib file
  bib2df(here("data", "my_publications.bib")) %>%
  mutate(MONTH = if_else(is.na(MONTH), "jan", MONTH),
    date = ymd(paste(YEAR, MONTH, "01", sep = "-"))) %>% 
  arrange(desc(date)) %>% 
  # put authors in one string
  mutate(author = map(AUTHOR, ~glue_collapse(.x, sep = "; "))) %>% 
  #underline my name
  mutate(author = str_replace(author, "Scott, E R", "\\\\underline{Scott, E R}")) %>% 
  mutate(author = str_replace(author, "Guo, M-M", "*Guo, M-M")) %>% 
  mutate(author = str_replace(author, "Agyei, A", "*Agyei, A")) %>% 
  mutate(
    journal = if_else(is.na(JOURNAL), BOOKTITLE, JOURNAL),
    doi = TeXencode(DOI),
    where = ifelse(
      !is.na(doi),
      glue("<journal>. \\url{http://doi.org/<doi>}", .open = "<", .close = ">"),
      journal)
    ) %>% 
  arrange(desc(YEAR))
```


```{r eval=FALSE, include=FALSE}
#don't like the format vitae produces, so I did it manually for now
detailed_entries(mypubs,
    what = author,
    when = YEAR,
    with = TITLE,
    where = where,
    .protect = FALSE
  )
```


```{r publications, eval=FALSE, include=FALSE}
bibliography_entries(here("data", "my_publications.bib")) %>%
  arrange(desc(issued))
```

\bigskip

**Software:**

\bigskip

**Scott ER** (2021) `bumbl`: Tools for modeling bumblebee colony growth and decline. https://CRAN.R-project.org/package=bumbl

\medskip

Szöcs E, Stirling T, **Scott ER**, Scharmüller A, and Schäfer RB (2020) `webchem`: Chemical Information from the Web. https://CRAN.R-project.org/package=webchem

\medskip

**Scott ER** (2019) `holodeck`: A Tidy Interface for Simulating Multivariate Data. https://CRAN.R-project.org/package=holodeck

\medskip

Contributor to Levin S. et al. (2022) `ipmr`: Integral Projection Models https://CRAN.R-project.org/package=ipmr


<!-- Would be good to update these soon -->
```{r eval=FALSE, include=FALSE}
df <- tribble(~what, ~when, ~with, ~where, ~why,
              "bumbl: Tools for modeling bumblebee colony growth",
              2021,
              "ER Scott",
              "https://cran.r-project.org/package=bumbl",
              "Author and maintainer",
              
              "webchem: retrieve chemical information from the web",
              2020,
              "E Szöcs, D Muench, J Ranke, ER Scott, J Stanstrup, R Allaway, Tamas Stirling",
              "https://cran.r-project.org/package=webchem",
              "Contributor and maintainer",
              
              "holodeck: A tidy interface for simulating multivariate data",
              2018,
              "ER Scott",
              "https://cran.r-project.org/package=holodeck",
              "Author and maintainer"
              )
```

```{r eval=FALSE, include=FALSE}
df %>% 
  arrange(desc(when)) %>% 
  detailed_entries(what = what, when = when, with = with, where = where, why = why)
```


# Teaching Experience

```{=html}
<!--# Teaching Interests
A sentence or two about the sorts of courses I'd like to teach.  Tailor to each job application
-->
```

```{r}
jobs %>%
  filter(Tag == "teaching", year(Start) > 2005) %>%
  arrange(desc(Start)) %>% 
  detailed_entries(
    what = What,
    when = When,
    with = With,
    where = Where,
    # why = Why, 
    .protect = FALSE)
```

\pagebreak
  
## Guest Lectures

```{r}
presentations %>% 
  filter(Tag %in% c("lecture")) %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}") %>% as.character(),
                   with = Conference,
                   where = Location,
                   why = Award)
```


# Mentoring Experience

  -	Ellie McDaniel (UF class of 2024) was a summer REU student working on the statistical assumptions and data limitations of applying distributed lag non-linear models to plant demographic analyses.
  -	Andrew Mercadante (UF class of 2022) was a summer REU student working on edge effects in fragmented tropical forests.
  -	Ji-Peng Wei (Masters student at Tea Research Institute) collaborated on four papers with me and was an integral collaborator for most of my PhD work. He went on to work in the tea industry China.
  -	Ming-Ming Guo (Zhejiang University class of 2018) helped carry out field experiments in China in 2018 and co-authored a publication. Ming-Ming was accepted into a PhD program at the Tea Research Institute in Hangzhou, China.
  -	Amma Agyei (Tufts class of 2022) conducted chemical analyses on tea samples and co-authored a publication. She was accepted to a combined BS/MS program in biomedical engineering at Tufts.
  -	Lan Ngo (Tufts class of 2018) piloted a research project to look for indirect effects of climate change in a microbially ripened tea product. She was hired as a Research Data Specialist at Dana-Farber Cancer Institute.
  -	Gabriel Taylor (Tufts class of 2018) accompanied me to China in 2017 to assist with fieldwork. After graduation, he worked for a labor union doing contract enforcement.
  -	Michelle Mu (Tufts class of 2018) piloted a machine learning method for detection of leafhopper damage in leaf scans. She went on to receive a MS from Northeastern and work as a research associate for a biotech firm.

# Grants

```{r}
awards %>%
  filter(tag == "grant") %>%
  detailed_entries(what = award, when = glue("{month(date, label = TRUE)} {year(date)}"),
                   why = amount) %>% 
  mutate(across(everything(), as.character)) %>% 
  mutate(with = as.character(with),
         when = as.character(when),
         where = as.character(where))
```

# Awards and Honors

```{r}
 awards %>% 
  filter(!tag %in% c("failed", "travel", "grant")) %>% 
  brief_entries(what = award, 
                when = glue("{month(date, label = TRUE)} {year(date)}"),
                with = with)
```




# Presentations

## Research Talks

```{r}
presentations %>%
  filter(Tag %in% c("talk", "invited")) %>%
  arrange(desc(When)) %>%
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Conference,
                   where = Location,
                   why = Award,
                   .protect = FALSE)
```

## Posters

```{r}
presentations %>% 
  filter(Tag == "poster") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Conference,
                   where = Location,
                   why = Award,
                   .protect = FALSE)
```
# Professional Development

```{r}
development %>% 
  filter(str_detect(tag, "teaching") | str_detect(tag, "dei") | str_detect(tag, "mentoring")) %>% 
  arrange(desc(date)) %>% 
  brief_entries(
    what = title,
    when = glue("{month(date, label = TRUE)} {year(date)}"),
    with = location,
    .protect = FALSE
  )
```

# Outreach

```{r}
outreach %>%
  arrange(desc(sortdate)) %>%
  detailed_entries(when = When,
                   what = Title,
                   with = Organization,
                   where = Location,
                   why = Description)
```

# Service

**Manuscript Reviews**: Agronomy (1), Journal of Chemical Ecology (1), Ecological Entomology (3), International Journal of Climatology (2), Oecologia (1), Frontiers in Cellular and Infection Microbiology (1), BMC Plant Biology (2), Frontiers in Plant Science (3), Brazilian Journal of Botany (1)

\bigskip

```{r}
jobs %>%
  filter(Tag == "service") %>% 
  group_by(What) %>% 
  summarize(across(c(When, With, End), first)) %>% 
  arrange(desc(End)) %>% 
    brief_entries(
      what = What,
      when = When,
      with = With
    )
```

<!-- ## Presented Workshops -->

```{r eval=FALSE, include=FALSE}
presentations %>% 
  filter(Tag == "workshop") %>% 
  arrange(desc(When)) %>% 
  brief_entries(
    what = Title,
    when = glue("{month(When, label = TRUE)} {year(When)}"),
    with = Conference,
    # where = Location,
    # why = Award
  )
```

