---
name: Eric Scott
docname: "Update"
position: "PhD Candidate"
address: "Department of Biology, Tufts University"
phone: +1 925-788-9855
www: ericrscott.com
email: "Eric.Scott@tufts.edu"
twitter: LeafyEricScott
github: Aariq
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
```

```{r experience, inclue=FALSE}
jobs.raw <- read_csv(here::here("data", "jobs.csv"))
jobs <-
  jobs.raw %>% 
  fill(Start, End, What, With, Where, Tag) %>%  
  mutate(Start = mdy(Start),
         End = mdy(End)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--Present") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  ))
```

```{r presentations, include=FALSE}
presentations.raw <- read_csv(here("data", "presentations.csv"))
presentations <- 
  presentations.raw %>% 
  mutate(When = mdy(When))
```

```{r awards, include=FALSE}
awards.raw <- read_csv(here("data", "awards and grants.csv"))
awards <- 
  awards.raw %>% 
  mutate(date = mdy(date)) %>% 
  mutate(when = glue("{month(date, label = TRUE)} {year(date)}"))
```


# Publications

```{r publications}
scholar::get_publications("kPEDEO0AAAAJ") %>%
  arrange(desc(year)) %>%
  filter(journal != "Whitman College") %>% 
  # filter(year >2018) %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

# Conferences and Presentations

```{r}
presentations %>%
  filter(When > ymd("2018-10-01"), Tag == "talk") %>% 
  add_row(When = "2019-1-17", Title = "[no presentation]", Authors = NA, Conference = "rstudio::conf 2019") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(
    what = Title,
    when = glue("{month(When, label = TRUE)} {year(When)}"),
    with = Conference,
    where = Location,
    why = Award
  )
```



# Teaching

```{r}
jobs %>%
  filter(Tag == "teaching", year(Start) > 2017) %>%
  arrange(desc(year(Start))) %>% 
  mutate(When = glue("Spring {When}")) %>% 
  detailed_entries(
    what = What,
    when = When
  ) 
```


```{r}
presentations %>%
  filter(year(When) > 2018, Tag == "lecture") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(
    what = Title,
    when = glue("{month(When, label = TRUE)} {year(When)}"),
    with = Conference,
    where = Location
  )
```

# Awards and Honors

```{r}
awards %>% 
  filter(year(date) > 2018) %>% 
  arrange(desc(date)) %>% 
  brief_entries(
    what = award,
    when = when,
    with = with
  )
```

# Other Updates

- Applied for internship at RStudio, was offered interview, but declined due to time requirement.
- Visited Gervay-Hague lab at UC Davis and was offered help writing a grant for a post-doc position there.
- I've heard from several researchers using my leafhopper egg finding method.
- I've decided not to use my 2017 leafhopper density experiment (potted plants, QXDM cultivar) for an example in the multivariate statistics paper. Instead, I'll include it with the 2018 data (mature plants, LJ and JGY cultivars).

# Dissertation Outline

1. Differential Changes in Tea Quality as Influenced by Insect Herbivory (book chapter, published)
2. Using the right tool for the job: Partial least squares as an alternative to principle component regression for analysis of multivariate data in ecology.
3. Interactive effects of drought severity and simulated herbivory on tea (*Camellia sinensis*) volatile and non-volatile metabolites	(published)
4. Effects of tea green leafhopper (*Empoasca onukii*) density on metabolites in different tea cultivars with implications for tea quality.
5. Interactive effects of elevated CO~2~ and insect herbivory on tea plant metabolism.
6. Climate impacts on leafhopper population growth in tea fields
6. Conclusion

\pagebreak

# Timeline
## January/February

- Consider using 2017 leafhopper data for example dataset in multivariate statistics paper [**DONE**]
    + I decided **not** to use it
- Begin mentoring BIO 94 student to get data for leafhopper experiments [**DONE**]

## March

- Finish analysis report for CO~2~ x herbivory paper [**DONE**]
- Finish analysis for multivariate statistics paper [**DONE**]
- ~~Submit multivariate stats paper to Oecologia~~

## April

- Finish complete draft of multivariate stats paper (April 8)
- Submit multivariate stats paper to Oecologia
- Finish LC/MS for 2017 and 2018 leafhopper density experiments (Week of April 8)

## May

- Mentee finishes leafhopper density paper (total phenolics and LC/MS compounds vs. density)
- Finish analysis of GC/MS and LC/MS data for leafhopper density experiments
- Draft of leafhopper density paper (for Frontiers in Plant Science special issue or Chemical Ecology)

## June/July

- Submit leafhopper density paper (June 15)
- Begin working on ***either*** CO~2~ x herbivory manuscript ***or*** leafhopper population growth manuscript

## August

- submit lefhopper population growth paper

# October

- Submit CO~2~ x Herbivory paper

# December

- Submit thesis
  